Notes and approaches to OCR

### 2020-08-19 outputs/documents/paper.Rmd
Clarify that Kraken only runs on Linux OS

| OCR Tool                             | Company	 | Type           |	Pricing |	Tech Requierements |
| ------------------------------------ | --------- | -------------- | ------- | ------------------ |
| Azure Cognitive Services (OCR)       | Microsoft | API		        |         |                    |
| Amazon Rekognition	                 | Amazon	   | API		        |         |                    |
| Tesseract		                         |           | R library      | Free	  |                    |
| OpenCV		                           |           | Python Library | Free	  |                    |
| Watson Visual Recognition	           | IBM	     | API		        |         |                    |
| Kraken		                           |           | Python Library	| Free	  |                    |
| Google Vision (for Text recognition) | Google	   | API		        |         |                    |
| SwiftOCR	(iOS)                      | Apple	   | Swift Library  |         |                    | 		
| Amazon Textract	                     | Amazon	   | API		        |         |                    |
|	Tensorflow                           | Google    | Python Library | Free    |                    |

@@

>>>>

| OCR Tool                             | Company	 | Type           |	Pricing |	Tech Requierements |
| ------------------------------------ | --------- | -------------- | ------- | ------------------ |
| Azure Cognitive Services (OCR)       | Microsoft | API		        |         |                    |
| Amazon Rekognition	                 | Amazon	   | API		        |         |                    |
| Tesseract		                         |           | R library      | Free	  |                    |
| PyTesseract (Wrapper Google's OCR Engine)    |           | Python Library | Free    |                    |
| OpenCV		                           |           | Python Library | Free	  |                    |
| Watson Visual Recognition	           | IBM	     | API		        |         |                    |
| Kraken	(Linux OS)                   |           | Python Library	| Free	  |                    |
| Google Vision (for Text recognition) | Google	   | API		        |         |                    |
| SwiftOCR	(iOS)                      | Apple	   | Swift Library  |         |                    | 		
| Amazon Textract	                     | Amazon	   | API		        |         |                    |
|	Tensorflow                           | Google    | Python Library | Free    |                    |

@@

Diego's comment: From what I learned so far, it could be easiness (an API is more straightforward than a library), number of characters correctly recognized, flexibility (the opposite of easiness), and cost. Moreover, some APIs such as Google's groups more than one character, whereas Azure returns only one character per boundary.
